%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% coding: utf-8
%%% End:
% !TEX TS-program = pdflatexmk
% !TEX encoding = UTF-8 Unicode
% !TEX root = ../main.tex

The main goal is to implement a web-based ray tracer addressing the problem of the large number of variants for CAD-based product visualization leveraging data close to the production CAD models.

This section contains references to the implementation of the path tracer. References are formatted in a consistent manner and can be searched for in the code. All relevant places are marked in code using the same reference. For example \coderef{100} refers to the code with the comment \textit{ref\#CODE-100}.

\section{Scene Description}
Lights, Materials, Camera, Objects
\section{Implementation}
\subsection{Ray Tracing}
\subsubsection{Uber Shader}

The OpenPBR standard is based on an über shader approach. This differs from node-based approaches such as MaterialX in that it uses a fixed set of inputs which can be configured. This approach offers a good balance between flexibility and performance.

\subsubsection{RGB, Spectral}
\subsubsection{Memory}

Memory Alignment (GPU), Memory Management (GPU+CPU)

\subsection{View Projection}

\todo{Move to Rasterization? Highlight difference between usage in Rasterization + Ray Tracing.}
In order to render an image, a virtual camera needs to be defined. Given a vertex as $p = (x, y, z)$, the view projection is responsible for transforming the vertex into normalized device coordinates. The view projection matrix is a 4x4 matrix which depends on the projection type.

Depending on the use case, different types of camera projection can be used. The most common types are perspective and orthographic projection. Perspective projection simulates the way the human eye perceives the world, objects which are further away appear smaller. Whereas orthographic projection does not take the distance into account and objects appear the same size regardless of their distance.

For many applications, especially photorealistic rendering, perspective projection is used. Therefore, the path tracer uses perspective projection. However, orthographic projection is frequently used in domains such as architecture.

These two projection types differ in the view projection matrix. For perspective projection, given $near$, $far$, $fov$, $aspectRatio$ as well as 

\begin{equation}
    \label{eqn:perspectiveProjectionHeight}
    height = 2 \cdot \mathit{near} \cdot \tan(\frac{1}{2} \underbrace{\pi / 180}_{\text{deg to rad}} \mathit{fov})
\end{equation}

as well as $width = aspectRatio \cdot height$, and $depth = far - \mathit{near}$, the matrix is defined as:

\begin{equation}
\begin{bmatrix}
    2\frac{\mathit{near}}{width} & 0 & 0 & 0 \\
    0 & 2\frac{\mathit{near}}{height} & 0 & 0 \\
    0 & 0 & - \frac{far + \mathit{near}}{depth} & -2 \frac{far \cdot \mathit{near}}{depth} \\
    0 & 0 & -1 & 0
\end{bmatrix}
\end{equation}

See \coderef{200} for implementation.

\subsection{Random Number Generator}

To simulate light transport, the path tracer needs to pick random directions. Generating a random direction vector, defined as $v = (x, y, z)$, can be achieved by picking three random numbers independent of one another. This is done using a random number generator (RNG). Unlike other programming languages, WGSL does not have a built-in RNG. Therefore, a custom RNG is required. There are a variety of RNGs available which differ in important characteristics. Some of the characteristics to consider when choosing a suitable RNG are:

\begin{itemize}
    \item{Statistical Quality} – The RNG should generate numbers that are statistically random. This means that the numbers should be uniformly distributed and have a low correlation between them.
    \item{Period} – The length of the cycle before the sequence of generated numbers starts to repeat itself.
    \item{Time Performance} – The time it takes to generate a random number. This is influenced by the algorithm as well as the hardware which may support dedicated instructions.
    \item{Space Usage} – The amount of memory required to store state.
\end{itemize}

Based on the use case, other factors such as prediction difficulty or others such as highlighted by O’Neill \cite{o2014pcg} may be important. Cryptography for example requires randomness of the RNG to prevent an adversary from predicting secret keys. Options to generate the randomness require additional signals \cite{randomnessCryptography} or may require special hardware such as LavaRand \cite{cloudflareLavaRand}. Many generators are pseudorandom generators. These generators are deterministic and require a seed to start the sequence. For crypographically secure generators, the seed must be random.
However, for a path tracer, there is no need for cryptographic security. Instead, it is more important to have high performance and having a long period to avoid repetition. Therefore, a pseudorandom number generator with non-cryptographically secure seed is used.

One option for such a pseudorandom generator is using Xorshifts such as described by Marsaglia \cite{marsaglia2003xorshift}. The algorithm can be defined as shown in Figure \ref{code:xorShift}. $x$ is the state of the RNG and $a$, $b$ and $c$ are constants which are chosen to achieve good statistical properties. Frequent choices for these constants are $a = 13$, $b = 17$ and $c = 5$.

\begin{figure}[H]
\begin{lstlisting}[style=wgsl]
x ^= x << a;
x ^= x >> b;
x ^= x << c;
\end{lstlisting}
\caption{Xorshift RNG implementation in WGSL.}
\label{code:xorShift}
\end{figure}

Alternatives to Xorshift are available, such as the Mersenne Twister \cite{rngMersenneTwister}. The Mersenne Twister is a pseudorandom number generator which has a long period and good statistical properties. However, it is slower than Xorshifts \cite{o2014pcg}. More recently, PCG has been proposed as an alternative to these options. PCG is a family of fast generators. The path tracer uses PCG-RXS-M-XS variant as described by O’Neill \cite{o2014pcg}. See \coderef{100} for implementation.

\subsection{WebGPU}
\subsection{Integration}
\section{Use Case Scenarios}
\section{Performance}